Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-16 paper/ms.tex
added new references for the intro

Some theoretical approaches to this problem have been based on a
forward modelling. Starting from the DM halo population, the
corresponding intrinsic star formation properties are infered and
statistics such as the luminosity function, the correlation function
and the equivalent width distributions. Such modelling has been
implemented from analytic considerations, semi-analytic models and
full N-body hidrodynamical simulations \citep{ForeroRomero2011}.

Added to the uncertainties in the astrophysical processeses describing
star formation in galactic populations, a highly debated steps in this
approach is the calculation of the fraction of Lyman-$\alpha$ photons
that escape the galaxy to the observer. Given the resonance nature of
the line, the radiative transfer of Lyman-$\alpha$ is sensitive to the
density, temperature, topology and kinematics of the neutral Hydrogen
in the interstellar medium (ISM).

>>>>

Some theoretical approaches to this problem have been based on a
forward modeling. Starting from the DM halo population, the
corresponding intrinsic star formation properties are infered and
statistics such as the luminosity function, the correlation function
and the equivalent width distributions. Such modelling has been
implemented from analytic considerations, semi-analytic models
 and 
full N-body hidrodynamical simulations
\citep{Dayal2009, ForeroRomero2011, Yajima2012, ForeroRomero2012} .

Added to the uncertainties in the astrophysical processeses describing
star formation in galactic populations, a highly debated steps in this
approach is the calculation of the fraction of Lyman-$\alpha$ photons
that escape the galaxy to the observer. Given the resonance nature of
the line, the radiative transfer of Lyman-$\alpha$ is sensitive to the
density, temperature, topology and kinematics of the neutral Hydrogen
in the interstellar medium (ISM) \citep{Neufeld1991, ForeroRomero2011,
Laursen2013}.
